A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2011-08-15 papers/contact/paper.tex
add test for convolution of convolution
Tested-on: bingley (Linux 2.6.32-5-amd64)
add a few more tests and plot a larger sphere

\begin{figure}
  \includegraphics[height=5cm]{figs/sphere-radial-08-13}
  \caption{Density and contact densities of fourteen hard spheres in a
    spherical cavity with radius 8.}
  \label{fig:sphere-density2}
\end{figure}

@@

The derivatives oof the remaining scalar densities can be reduced to
sums of the terms above:
\begin{align}
  n_1(\mathbf{r}) &= \int \mathbf{dr'} \frac{n(\mathbf{r'})}{4\pi R(\mathbf{r'})}
  \delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'})) \\
  \frac{\delta n_1(\mathbf{r})}{\delta R(\mathbf{r}')}
  &= \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})}\delta'(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
  -
  \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^2}\delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
\end{align}
\begin{align}
  n_0(\mathbf{r}) &= \int \mathbf{dr'} \frac{n(\mathbf{r'})}{4\pi R(\mathbf{r'})^2}
  \delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'})) \\
  \frac{\delta n_0(\mathbf{r})}{\delta R(\mathbf{r}')}
  &= \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^2}\delta'(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
  -2
  \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^3}\delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
\end{align}

>>>>

\begin{figure}
  \includegraphics[height=5cm]{figs/sphere-radial-08-13}
  \caption{Density and contact densities of fourteen hard spheres in a
    spherical cavity with radius 8.  Also similar densities of spheres
    in even larger cavities.}
  \label{fig:sphere-density2}
\end{figure}

@@

The derivatives of the remaining scalar densities can be reduced to
sums of the terms above:
\begin{align}
  n_1(\mathbf{r}) &= \int \mathbf{dr'} \frac{n(\mathbf{r'})}{4\pi R(\mathbf{r'})}
  \delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'})) \\
  \frac{\delta n_1(\mathbf{r})}{\delta R(\mathbf{r}')}
  &= \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})}\delta'(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
  -
  \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^2}\delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
\end{align}
\begin{align}
  n_0(\mathbf{r}) &= \int \mathbf{dr'} \frac{n(\mathbf{r'})}{4\pi R(\mathbf{r'})^2}
  \delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'})) \\
  \frac{\delta n_0(\mathbf{r})}{\delta R(\mathbf{r}')}
  &= \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^2}\delta'(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
  -2
  \frac{n(\mathbf{r'})}{4\pi
    R(\mathbf{r'})^3}\delta(|\mathbf{r}-\mathbf{r'}| - R(\mathbf{r'}))
\end{align}
